---
title: "deliverable1"
author: "Austin Meyer"
date: "10/10/2019"
output: html_document
---

# Introduction

### Hello
  Hello my name is Austin Meyer. For my Data Science course at CSU Chico I wanted to investigate data from the US about the economy and politics. I chose this area because, it 

### Chosen Data Set
  The dataset has been acquired from [FiveThirtyEight]("https://projects.fivethirtyeight.com/2018-midterm-election-forecast/house/#history") an ABC company. By the looks of their data they have a left tilt when looking for data to showcase. How I justified this assumption is based on how many political data sets they started working with from their inseption in 2014 up to 2016. Then how many political data sets they started working with after the election on 2016.The data set I found is polling data, which means only people who want to take the poll have been recorded. With that in mind lets move on to some clearifications in the data.
  
### What Do These Columns Mean

  Some of the columns in this data may be confusing, at least some where too me. The columns that make up most of the confusion are the p10_voteshare and p90_voteshare. I looked it up and found a pretty good article that explanes it better than I can: [What do p10 and p90 mean]("https://blogs.dnvgl.com/software/2016/12/p10-p50-and-p90/"). In the case of our data a p10 voteshare means that 10% of the vote share will exceed x (x being the number). A p90 discribes that 90% of the voteshare will exceed this value.
  
  * Forcast date is when the election was supposed to take place, which has already happened.
  
  * State is straight forward. It is the state in which the canadite was running.
  
  * District is also straight forward. This is the district in which the canadite was running in a certian state.
  
  * The special elections column will be TRUE if a special election happend that election.


# Getting Started With Data Cleaning

### Download packages

  First we will download necessary packages to recreate the data sets I will have and be investigating. We will be first installing the wonderful tidyverse. The tidyverse package will help us bring order too messed up data.
```{r}
# These three will import many of the commands we will use to clean our data
# install.packages("tidyverse")
library("tidyverse")
library("tidyr")
# Will help us in manipulating our datasets
library("dplyr")
# Helps us read files from the web
library("readr")
# This library will help us visualize the data
library("ggplot2")
```


### Loading The Data

  Finally we get to load the data into our Rstudio set up. If you don't already have R and Rstudio please follow these two links and follow their download processes:
  * [R download (The langauge library)]("https://cran.r-project.org/mirrors.html")
    + Don't be afraid of all the links, just scroll down to one nearest to you
  *[Rstudio download]("https://rstudio.com/products/rstudio/download/#download")
  
  Now were ready to move on to downloading the data.The line bellow will turn the data into R readable data.
```{r}
national_data <- read_csv("https://projects.fivethirtyeight.com/congress-model-2018/house_district_forecast.csv")
```

Looking over the data there are a few things we need to clean up. One of those is to make sure the time is in POSIX time, which is just a standardized way of writing time.Luckly the date is already in the form we desire.


We also need to remove the models column. It is used specifically for the website that the data was pulled from. We will do this by selecting everything, but the model column.
```{r}
national_data <- select (national_data,-c(model))
```

# Early Assessment and Visualization

  The first questions I had when looking at this data is: What were the probable vote shares of incumbent canadites. First I had to create a new table that was filled with just the incubents.
```{r}
incumbent_chances <- tibble(candidate=national_data$candidate[national_data$incumbent == TRUE], win_probability=national_data$win_probability[national_data$incumbent == TRUE], voteshare=national_data$voteshare[national_data$incumbent == TRUE])
```

  Next I greated a histograph, which shows use were the voteshares fall for the incumbents.
```{r}
visualIncumbent + geom_histogram(bins = 100)
```

  This graph tells us a lot about how incumbents faired in the last election. Many of them had above 50% of the vote shares. The real question though is what keeps them in office. Is it a lack of a better candidate or are they representinng their districts well.


