---
title: "Assessing the House Election of 2020" #replace the title with something short and catchy to represent your project
subtitle: "Austin's Data Science Portfolio" #replace blank with your name
output:
  html_document:
    df_print: paged
---

# <style="color: #66B2FF;">Introduction</ style>

### Hello
  Hello my name is Austin Meyer. For my Data Science course at CSU Chico I wanted to investigate data from the US about the economy and politics. I chose this area because, it 

### Chosen Data Set
  The dataset has been acquired from [FiveThirtyEight]("https://projects.fivethirtyeight.com/2018-midterm-election-forecast/house/#history") an ABC company. By the looks of their data they have a left tilt when looking for data to showcase. How I justified this assumption is based on how many political data sets they started working with from their inseption in 2014 up to 2016. Then how many political data sets they started working with after the election on 2016.The data set I found is polling data, which means only people who want to take the poll have been recorded. With that in mind lets move on to some clearifications in the data.
  
### What Do These Columns Mean

  Some of the columns in this data may be confusing, at least some where too me. The columns that make up most of the confusion are the p10_voteshare and p90_voteshare. I looked it up and found a pretty good article that explanes it better than I can: [What is p10 and p90 mean]("https://blogs.dnvgl.com/software/2016/12/p10-p50-and-p90/"). In the case of our data a p10 voteshare means that 10% of the vote share will exceed x (x being the number). A p90 discribes that 90% of the voteshare will exceed this value.
  
  Forcast date is when the election was supposed to take place, which has already happened.
  
  State is straight forward. It is the state in which the canadite was running.
  
  District is similar to state. This is the district in which the canadite was running.
  
  There were a few special elections and this tag would describe those elections.


# Getting Started With Data Cleaning

### Download packages

  First we will download necessary packages to recreate the data sets I will have and be investigating. We will be first installing the wonderful tidyverse. The tidyverse package will help us bring order too messed up data.
```{r}
install.packages("tidyverse")
library("tidyverse")
```


  In all honesty I have forgotten what these do come back to them.
```{r}
library("tidyr")
library("dplyr")
library("readr")
```


### Loading The Data

  Finally we get to load the data into our Rstudio set up. If you don't already have R and Rstudio please follow these two links and follow their download processes:
  * [R download (The langauge library)]("https://cran.r-project.org/mirrors.html")
    + Don't be afraid of all the links, just scroll down to one nearest to you
  *[Rstudio download]("https://rstudio.com/products/rstudio/download/#download")
  
  Now were ready to move on to downloading the data.The line bellow will turn the data into R readable data.
```{r}
national_data <- read_csv("https://projects.fivethirtyeight.com/congress-model-2018/house_district_forecast.csv")

### 2. Model Planning and Building

Coming soon...

### 3. Results and Operationalization

Coming soon...

